---
title: "06 Starter Code"
format: docx
editor: visual
---

This file contains the code for Lecture 06: Linear Models.

Keep `home_goods_customers.csv` in your working folder. Read `data_dictionary.pdf` for the variable definitions. The data describe 10,000 customers of a fictional home-goods retailer and are semi-synthetic.

## Simulate Ben & Jerry's Spending

Our grocery-store example relates customer spending on Ben & Jerry's during a visit (`CustomerSpend`, dollars) to the price per pint (`Price`, dollars). We choose the hypothetical relationship `CustomerSpend = 24 - 2 * Price + error`, then simulate data to see whether fitting can recover the intercept and slope. This example is separate from the home-goods customer CSV; these are not its generating values.

```{r}
# Load packages.
library(tidyverse)

# Set the randomization seed to simulate the same data each time.
set.seed(42)

# Set the parameter values.
beta0 <- 24
beta1 <- -2

# Simulate data.
sim_data <- tibble(
  Price = runif(100, min = 3, max = 7),
  CustomerSpend = beta0 + beta1 * Price + rnorm(100, mean = 0, sd = 3)
)
```

## Plotting Our Simulated Data

```{r, fig.height=3.5}
# TODO: Make a scatterplot of CustomerSpend versus Price in sim_data, with labeled units.
# How does the pattern change when you change the simulation above?
```

## A Note on Reproducible Random Draws

`set.seed()` restarts the random-number sequence so the same code produces the same simulated data.

```{r}
# Successive draws usually differ.
rnorm(1)
rnorm(1)

# Restarting from the same seed repeats the draw.
set.seed(42)
rnorm(1)

set.seed(42)
rnorm(1)
```

## Using tidymodels

Specify the **model type** with `linear_reg()` and the **engine** (the implementation) with `set_engine("lm")`.

```{r, message=FALSE}
library(tidymodels)
```

```{r}
reg_model <- linear_reg() |> 
  set_engine("lm")
```

## Modeling Hypothetical Data

We chose the **exact** story behind how customer sales are determined in our hypothetical data.

So what results should we see from our model?

## Fit the Model

`fit()` uses the formula `outcome ~ explanatory variable`.

```{r}
reg_model <- reg_model |>
  fit(CustomerSpend ~ Price, data = sim_data)
```

## Inspect the Model

`tidy()` returns a table of parameter estimates.

```{r}
reg_model |>
  tidy()
```

How close are the estimates to our chosen values, 24 and -2? Why might they differ? Interpret the slope in dollars of customer spending per \$1 of price per pint.

## From Simulation to Customer Data

`HouseholdIncome` measures annual household income in dollars. `PreviousSpend` measures spending at this retailer over the previous 12 months.

```{r}
customers <- read_csv("home_goods_customers.csv", show_col_types = FALSE)

customer_model_data <- customers |>
  drop_na(HouseholdIncome, PreviousSpend) |>
  mutate(IncomeThousands = HouseholdIncome / 1000)
```

This leaves 9,800 customers. The 200 missing incomes are not zero incomes; today's model omits those customers.

## Plotting Customer Spending

```{r, fig.height=3.5}
customer_model_data |>
  ggplot(aes(x = IncomeThousands, y = PreviousSpend)) +
  geom_point(alpha = 0.15) +
  labs(x = "Annual household income ($1,000s)",
       y = "Previous 12-month spending ($)")
```

## Fit the Customer Model

```{r}
customer_model <- linear_reg() |>
  set_engine("lm") |>
  fit(PreviousSpend ~ IncomeThousands, data = customer_model_data)

customer_model |>
  tidy()
```

Focus on the `estimate` column. Interpret the slope in dollars of previous 12-month spending per \$1,000 of annual household income. It describes an association, not an established causal effect. The intercept is a prediction at zero income, outside the observed range of \$15,000 to \$350,000.

## More Than One Explanatory Variable

The formula `y ~ x1 + x2` includes two explanatory variables. Each slope describes a one-unit difference in its variable, holding the other included variable fixed. The slope coefficients are still associations.

## Live Coding Exercise

The home-goods retailer's leadership wants an additional analysis of how customer incomes and ages are related to past spending.

What could the relationship between age and spending look like?

Let's answer this question with a model.

```{r}

```
